Kelompok 4_Praktikum_Pekan 8

### 2024-04-08 Project/Kelompok 4_Praktikum_Pekan 8.Rmd
Update

@@

```{r}
print(norm_means)
```

>>>>

```{r fig.height=7, fig.width=15, dpi=300}
par(mfrow = c(1, 3))
hist(apply(norm_samples[[1]], 1, mean))
hist(apply(norm_samples[[2]], 1, mean))
hist(apply(norm_samples[[3]], 1, mean))
```

@@

```{r}
population <- rexp(1000)
means <- rep(NA, 1000)

 for (i in c(1:1000)) means[i] <- mean(rexp(100))

 str(means)

 str(norm_means)
```

```{r fig.height=7, fig.width=15, dpi=300}
set.seed(361)
k <- 100 # ulangan
sample_size <- c(2, 5, 25)

norm_samples <- lapply(sample_size, function(n) matrix(rnorm(n*k),k))

par(mfrow = c(2, 3))
hist(norm_samples[[1]], main = "Histogram Normal n=2", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#d9eacb")
hist(norm_samples[[2]], main = "Histogram Normal n=5", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#b4e69e")
hist(norm_samples[[3]], main = "Histogram Normal n=25", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#8DC16D")

norm_means <- list()

for (i in seq_along(sample_sizes)) {
  norm_means[[i]] <- apply(norm_samples[[i]], 1, mean)
}

hist(norm_means[[1]], main = "Histogram Normal n=2", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#d9eacb")
hist(norm_means[[2]], main = "Histogram Normal n=5", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#b4e69e")
hist(norm_means[[3]], main = "Histogram Normal n=25", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#8DC16D")
```

```{r}
norm_means[[1]] <- apply(norm_samples[[1]], 1, mean)
hist(rowMeans(matrix(rnorm(2000), ncol = 2)), main = "Rataan Contoh (n = 2)")
hist(rowMeans(matrix(rnorm(5000), ncol = 5)), main = "Rataan Contoh (n = 5)")
hist(rowMeans(matrix(rnorm(25000), ncol = 25)), main = "Rataan Contoh (n = 25)")
```
